Road Segment Prioritization for Bicycle Infrastructure

### 2020-11-20 README.Rmd
Update readme, reproduce
Changes for reproducibility

<!--   - Source: -->
<!--     <http://geoportal.statistics.gov.uk/datasets/826dc85fb600440889480f4d9dbb1a24_0> -->
<!--   - Location in Repo: data-raw/MSOA\_2011\_Boundaries/\[Add files here\] -->

@@

```{r desirefacetcycling, fig.cap="Current and Potential Cycling Demand", out.width="75%", fig.show='hold', echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/desire_facet_cycling.png")
```

@@

table <- readRDS("data/Manchester/graph_with_flows_weighted_communities.RDS")
# we weigh the flow on each edge by its distance. We can then get how much of the commuter km are satisfied
table$person_km <- table$flow * table$d
# get % of total person km on each link
table$person_km_perc <- (table$person_km / sum(table$person_km)) * 100

>>>>

<!--   - Source: -->
<!--     <http://geoportal.statistics.gov.datasets/826dc85fb600440889480f4d9dbb1a24_0> -->
<!--   - Location in Repo: data-raw/MSOA\_2011\_Boundaries/\[Add files here\] -->

@@

```{r desirefacetcycling, fig.cap="Current and Potential Cycling Demand", out.width="75%", fig.show='hold', echo=FALSE}
knitr::include_graphics("data/Manchester/Plodesire_facet_cycling.png")
```

@@

table <- readRDS("data/Manchester/graph_with_flows_weighted_communities.Rds")
# we weigh the flow on each edge by its distance. We can then get how much of the commuter km are satisfied
table$person_km <- table$flow * table$d
# get % of total person km on each link
table$person_km_perc <- (table$person_km / sum(table$person_km)) * 100
